### 2009-11-26 doc/manuals/janitor/tex_installation/installation.tex
Update for explaining how to list multiple catalog files.
fix typo

The parameter \texttt{enable} specifies whether the Janitor shall be used
within A-REX or not. Use the value \texttt{"0"} to disable Janitor. The
\texttt{uid} and the \texttt{gid} are defining which effective user id
(uid) and group id (gid) shall be used for the Janitor.\footnote{For
the time speaking, you need to have started the ARC services as root to
allow the Janitor to change into those IDs.} The \texttt{registrationdir}
describes the directory in which the subdirectories \texttt{jobs} and
\texttt{rtes} will be created.  In these directories the states of the
jobs and the runtime environments will be stored.  The knowledge base
of installable packages is specified by the parameter \texttt{catalog}.
Its value can be any kind of URL pointing to a file written in the
Resource Description Framework (RDF) format.  The specification of the
RDF file will be explained in detail in section~\ref{sec:catalog}.
The parameter \texttt{downloaddir} assigns the directory in which
the installation files will be saved after they have been downloaded
or copied from the repository which was specified by the catalog. The
\texttt{installationdir} finally specifies the directory into which all
packages will be installed and should be available for all computing
elements, i.e.\ by using a shared volume.  If the configuration file
furthermore contains the \texttt{runtimedir} tag within the section
\texttt{grid-manager}, the Janitor will also create a symbolic link
in the \texttt{runtimedir} pointing to the configuration script of the
installation performed by the Janitor.  The tags \texttt{jobexpirytime}
and \texttt{rteexpirytime} are used for an automated cleanup and is
defined in seconds.  The default value for the \texttt{jobexpirytime} is
seven days and for the \texttt{rteexpirytime} three days.  The additional
tags \texttt{allow\_base} \texttt{deny\_base} \texttt{allow\_rte} and
\texttt{deny\_rte} are used to include or exclude certain base packages
or runtime environments of the catalog. This feature is useful, if
the catalog is maintained by a higher organization.  The path to the
log4perl configuration file is defined by the tag \texttt{logconf}.
An example how to configure ARC and log4perl is provided in the
Listings~\ref{lst:arc_conf} and ~\ref{lst:log_conf}.

@@

>>>>

The parameter \texttt{enabled} specifies whether the Janitor shall be used
within A-REX or not. Use the value \texttt{"0"} to disable Janitor. The
\texttt{uid} and the \texttt{gid} are defining which effective user id
(uid) and group id (gid) shall be used for the Janitor.\footnote{For
the time speaking, you need to have started the ARC services as root to
allow the Janitor to change into those IDs.} The \texttt{registrationdir}
describes the directory in which the subdirectories \texttt{jobs} and
\texttt{rtes} will be created.  In these directories the states of the
jobs and the runtime environments will be stored.  The knowledge base
of installable packages is specified by the parameter \texttt{catalog}.
Its value can be any kind of URL pointing to a file written in the
Resource Description Framework (RDF) format.  The specification of the
RDF file will be explained in detail in section~\ref{sec:catalog}.
The parameter \texttt{downloaddir} assigns the directory in which
the installation files will be saved after they have been downloaded
or copied from the repository which was specified by the catalog. The
\texttt{installationdir} finally specifies the directory into which all
packages will be installed and should be available for all computing
elements, i.e.\ by using a shared volume.  If the configuration file
furthermore contains the \texttt{runtimedir} tag within the section
\texttt{grid-manager}, the Janitor will also create a symbolic link
in the \texttt{runtimedir} pointing to the configuration script of the
installation performed by the Janitor.  The tags \texttt{jobexpirytime}
and \texttt{rteexpirytime} are used for an automated cleanup and is
defined in seconds.  The default value for the \texttt{jobexpirytime} is
seven days and for the \texttt{rteexpirytime} three days.  The additional
tags \texttt{allow\_base} \texttt{deny\_base} \texttt{allow\_rte} and
\texttt{deny\_rte} are used to include or exclude certain base packages
or runtime environments of the catalog. This feature is useful, if
the catalog is maintained by a higher organization.  The path to the
log4perl configuration file is defined by the tag \texttt{logconf}.
An example how to configure ARC and log4perl is provided in the
Listings~\ref{lst:arc_conf} and ~\ref{lst:log_conf}.

@@

When working with several catalogs, then the multiple catalog lines can
be placed into the same arc.conf file. But every must go into its own block
as separated with \[janitor/someName\] directives.
